---
title: "Housing Value in Suburbs of Boston"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(MASS)
library(corrplot)
```

```{r}
str(Boston)
summary(Boston)
corrplot(cor(Boston))
```

#We can see that:  
rm (Average number of rooms per dwelling) strongly and positively affects medv.
lstat strongly and negatively affects medv
some variables positively affects medv:  
* zn (proportion of residential land zoned for lots over 25k sq ft)  
* chas (bounds river or not)  
* dis (weighted distance to Boston employment centres)  
* black (proportion of black by town)  

some variable negatively affects medv:  
* crim (criminal rate)  
* indus (non retail biz acres per town)  
* nox (NO2 concentration)  
* age ( of the town)  
* rad (accessibility to radial highways)
* tax (full value property tax rate)
* ptratio (pupil teacher ratio by town)

```{r}
#Predict per capita rate crime based on other variable
lm.fit = lm(crim ~ ., data = Boston)
summary(lm.fit)
```

```{r}
varlist <- names(Boston)[2:14]
models <- lapply(varlist, function(x) {
  lm(substitute(crim ~ i, list(i = as.name(x))), data = Boston)
})
lapply(models, summary)
```
All variables are significant except chas.

```{r}
lm.fit_mlr = lm(crim ~ ., data = Boston)
summary(lm.fit_mlr)
```
We can reject null hypothesis with variables: zn, dis, rad, black, medv

```{r}
summary(Boston$crim)
hist(Boston$crim)
boxplot(Boston$crim)
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

