---
title: "R Notebook"
output: html_notebook
---
COMPREHENSIVE WORK ON LINEAR MODEL
* Fit a model with both quantitative and qualitative predictors
* Interaction between predictors
* Binnarize categorical predictors using dummyVar()
* Select useful features using stepAIC()
* Generate and interprete plot for LM
* Implement Ridge and Lasso using glmnet() and cv.glmnet()

Dataset to use: Credit
```{r}
library(ISLR)
data(Credit)
Credit$ID <- NULL
sample(Credit)
```

```{r}
summary(Credit)
```

Exploratory Data Analysis

```{r}
 # Set 
p1 <- ggplot(data = Credit, mapping = aes(x = log(Income))) + 
  geom_histogram(fill = "blue")

p2 <- ggplot(data = Credit, mapping = aes(x = log(Limit))) + 
  geom_histogram(fill = "blue")

p3 <- ggplot(data = Credit, mapping = aes(x = log(Rating))) + 
  geom_histogram(fill = "blue")

p4 <- ggplot(data = Credit, aes(x = Cards)) + 
  geom_bar(fill = "blue")

p5 <- ggplot(data = Credit, aes(x = Age)) + 
  geom_histogram(fill = "blue")

p6 <- ggplot(data = Credit, aes(x = Education)) + 
  geom_bar(fill = "blue")

p7 <- ggplot(data = Credit, aes(x = Gender))  +
  geom_bar(fill = "blue")

p8 <- ggplot(data = Credit, aes(x = Student)) + 
  geom_bar(fill = "blue")

p9 <- ggplot(data = Credit, aes(x = Ethnicity)) + 
  geom_bar(fill = "blue")

p10 <- ggplot(data = Credit, aes(x = log(Balance))) + 
  geom_histogram(fill = "blue")

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, ncol = 4)

```
